---
title: "Patient-Specific Reference Data for PROMIS PF, UE, & PI"
subtitle: "5. Additional Information"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile, 
      encoding = encoding, 
      output_dir = "html") })
output:
  html_document:
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: lumen
    toc: yes
    toc_depth: 3
    toc_float: yes
---


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)

library(tidyverse)
library(summarytools)
library(readxl)
library(nord)
library(gghalves)
library(plotly)
library(ggExtra)
library(grid)
library(gridExtra)
library(viridis)
library(cowplot)
library(hrbrthemes)
library(officer)
library(flextable)
library(qwraps2)
library(MetBrewer)
library(ggpubr)
library(cowplot)
library(tableHTML)
```

# Setup
```{r, warnings = FALSE}
dataComplete <- readRDS("data/tidy/dataComplete.rds")
```

# Additional Information

## Figures

### Physical Functioning

<br>

#### By Country

##### Half Violin Plots
```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = factor(Country), y = pf_tscore, fill = Country)) +
  geom_half_violin(side = "r")   +
  #geom_violin()   +
  geom_jitter(height = 0.2, 
              width = 0.1, 
              color = "#3B4252",
              shape = 1) +
  theme_bw() +
  xlab("") + 
  ylab("T-Score") +
  scale_fill_nord("aurora") +
  coord_flip() +
  theme(legend.position="none")
```

<br>

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_tscore, fill = Country)) +
 # geom_half_violin(side = "r")   +
  #geom_violin()   +
  geom_histogram() +
  theme_bw() +
  xlab("") + 
  ylab("T-Score") +
  scale_fill_nord("aurora") +
  theme(legend.position="none")
```


#### By country and age group

```{r}
dataComplete %>% 
    mutate(Country = country_table) %>% 
  group_by(Country, agegroup) %>% 
  #select(pf_tscore) %>%
  ggplot(aes(x = factor(Country), y = pf_tscore, fill = Country)) +
  geom_half_violin(side = "r")   +
  theme_bw() +
  xlab("") + 
  ylab("tscore") +
  scale_fill_nord("aurora") +
  coord_flip() +
  facet_grid(vars(agegroup))
```

<br>

##### Density Plot A

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_tscore, color = Country)) +
  geom_density()   +
  theme_bw() +
  xlab("T-Score PROMIS PF 2.0 Custom Short-Form") + 
  ylab("density") +
  facet_grid(vars(agegroup)) + 
  scale_color_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60))
```

<br>

##### Density Plot B

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_tscore, group =Country, fill = Country)) +
  geom_density(adjust=1.5, alpha=.2) +
  theme_minimal() +
  xlab("T-Score PROMIS PF 2.0 Custom Short-Form") + 
  ylab("Density") +
  facet_grid(vars(agegroup)) + 
  scale_color_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60)) 
```

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_tscore, group =Country, fill = Country)) +
  geom_density(adjust=1.5, alpha=.2) +
  theme_minimal() +
  xlab("T-Score PROMIS PF 2.0 Custom Short-Form") + 
  ylab("density") +
  facet_grid(vars(agegroup)) + 
  scale_color_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60))
```

##### Boxplot

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_tscore, y = Country, fill = Country)) +
  geom_violin(alpha = .3) +
  geom_boxplot(width = .4, alpha = .3) +
  theme_minimal() +
  xlab("T-Score PROMIS PF 2.0 Custom Short-Form") + 
  facet_grid(vars(agegroup)) + 
  scale_fill_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60)) +
  theme(legend.position="none")
```

<br>

### Upper Extremities

#### Density Plots

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = ue_tscore, group =Country, fill = Country)) +
  geom_density(adjust=1.5, alpha=.2) +
  theme_minimal() +
  xlab("T-Score PROMIS UE 2.0 Custom Short-Form") + 
  ylab("Density") +
  facet_grid(vars(agegroup)) + 
  scale_color_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60)) 
```


### Pain interference

#### Half Violin Plots
```{r}
dataComplete %>% 
  group_by(country_table) %>% 
  select(pi_tscore) %>%
  ggplot(aes(x = factor(country_table), y = pi_tscore, fill = country_table)) +
  geom_half_violin(side = "r")   +
  geom_jitter(height = 0.2, 
              width = 0.1, 
              color = "#3B4252",
              shape = 1) +
  theme_bw() +
  xlab("") + 
  ylab("T-Score") +
  scale_fill_nord("aurora") +
  coord_flip() +
  theme(legend.position="none")
```


```{r}
dataComplete %>% 
  group_by(country_table, agegroup) %>% 
  select(pi_tscore) %>%
  ggplot(aes(x = factor(country_table), y = pi_tscore, fill = country_table)) +
  geom_half_violin(side = "r")   +
  theme_bw() +
  xlab("") + 
  ylab("tscore") +
  scale_fill_nord("aurora") +
  coord_flip() +
  facet_grid(vars(agegroup))
```

<br>

#### Density Plots

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pi_tscore, group =Country, fill = Country)) +
  geom_density(adjust=1.5, alpha=.2) +
  theme_minimal() +
  xlab("T-Score PROMIS PI Custom Short-Form") + 
  ylab("Density") +
  facet_grid(vars(agegroup)) + 
  scale_color_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60)) 
```
##### Boxplot

```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pi_tscore, y = Country, fill = Country)) +
  geom_violin(alpha = .2) +
  geom_boxplot(width = .4, alpha = .2) +
  theme_minimal() +
  xlab("T-Score PROMIS pi 2.0 Custom Short-Form") + 
  facet_grid(vars(agegroup)) + 
  scale_fill_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60)) +
  theme(legend.position="none")
```


```{r}
dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pi_tscore, group = Country, fill = Country)) +
  geom_density(adjust=1.5, alpha=.2) +
  theme_minimal() +
  xlab("T-Score PROMIS PI Custom Short-Form") + 
  ylab("density") +
  facet_grid(vars(agegroup)) + 
  scale_color_nord("victory_bonds") +
  scale_x_continuous(breaks=c(20, 30, 40, 50, 60))
```

<br>

### Correlation UE - PF

```{r}
dataComplete %>%  
  ggplot(aes(x = pf_tscore, y = ue_tscore)) +
  geom_point(shape = 1) +
  geom_smooth(method=lm, se=F) +
  theme_classic() + 
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE) +
  labs(x = "PROMIS PF 2.0 T-Score", y = "PROMIS UE 2.0 T-Score", 
       title ="Correlation PROMIS Physical Functioning - Upper Extremities",
       subtitle = "",
       caption = "",
       alt = "")
```

#### By age group
```{r}
dataComplete %>%  
  ggplot(aes(x=pf_tscore, y=ue_tscore, color = agegroup)) +
  geom_point(shape = 1) +
  geom_smooth(method=lm, se=F) +
  theme_classic() + 
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE) +
  labs(color = "Age Group",
       x = "PROMIS PF 2.0 T-Score", y = "PROMIS UE 2.0 T-Score", 
       title ="Correlation PROMIS Physical Functioning - Upper Extremities",
       subtitle = "By Age Group",
       caption = "",
       alt = "") 
```


```{r}
cor(dataComplete$pf_tscore, dataComplete$ue_tscore,  method = "pearson", use = "complete.obs")

p <- ggscatter(dataComplete, x = "pf_tscore", y = "ue_tscore", 
          add = "reg.line", 
          add.params = list(color = "#5E81AC", fill = "lightgray"),
          conf.int = TRUE, 
          cor.method = "pearson",
          xlab = "PF 2.0 Custom SF", 
          ylab = "UE 2.0 Custom SF",
          alpha = .7,
          ) + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01) 


ggMarginal(p, type="histogram", fill = "#D08770", xparams = list(  bins=20))
```

<br>

#### Differences between PF scale and UE subscale

```{r}
difference_density <- dataComplete %>% 
  mutate(diff_pf_ue = pf_tscore - ue_tscore) %>% # negative: better UE than PF, positive: better PF than UE
  relocate(diff_pf_ue) %>% 
  arrange(diff_pf_ue) %>% 
  ggplot(aes(x = diff_pf_ue)) +
  geom_density() +
  geom_text(x=10, y=0.06, label="PF > UE") + 
  geom_text(x=-10, y=0.06, label="UE > PF") +
  theme_minimal() + 
  scale_x_continuous(limits=c(-20, 20))
```

```{r}
difference_boxplot <- dataComplete %>% 
  mutate(diff_pf_ue = pf_tscore - ue_tscore) %>% # negative: better UE than PF, positive: better PF than UE
  relocate(diff_pf_ue) %>% 
  arrange(diff_pf_ue) %>% 
  ggplot(aes(x = diff_pf_ue)) +
  geom_boxplot() +
  #geom_text(x=10, y=0.3, label="PF > UE") + 
  #geom_text(x=-10, y=0.3, label="UE > PF") +
  theme_minimal() + 
  scale_x_continuous(limits=c(-20, 20))

grid.arrange(difference_density, difference_boxplot, ncol=1)
```
<br>


```{r}
p1 <- difference_density  + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2 <- difference_boxplot +
  xlab("Difference PF 2.0 Custom SF - UE Custom SF")
legend <- get_legend(p1)   # get the legend of the first one plot

# here the plots in a grid
prow <- plot_grid( p1 + theme(legend.position="none"),
           # here you add the percentage
           p2 + theme(legend.position="none") + scale_y_continuous(labels = scales::percent),
           align = 'v',
           labels = c("A", "B"),
           hjust = -1,
           nrow = 2)

# here you add the legend
p <- plot_grid( prow, legend, rel_widths = c(3, .3))
p
```

```{r}
pf_ue_diff_larger_10 <- dataComplete %>% 
  mutate(diff_pf_ue = pf_tscore - ue_tscore) %>% # negative: better UE than PF, positive: better PF than UE
  relocate(diff_pf_ue) %>% 
  arrange(diff_pf_ue) %>% 
  filter(abs(diff_pf_ue) > 10)
pf_ue_diff_larger_10
```

```{r}
nrow(dataComplete) / nrow(pf_ue_diff_larger_10)
```

### Correlation Pf - PI

```{r}
dataComplete %>%  
  ggplot(aes(x = pf_tscore, y = pi_tscore)) +
  geom_point(shape = 1) +
  geom_smooth(method=lm, se=F) +
  theme_classic() + 
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE) +
  labs(x = "PROMIS PF 2.0 T-Score", y = "PROMIS PI T-Score", 
       title ="Correlation PROMIS Physical Functioning - Pain interference",
       subtitle = "",
       caption = "",
       alt = "")
```

#### By age group
```{r}
dataComplete %>%  
  ggplot(aes(x=pf_tscore, y=pi_tscore, color = agegroup)) +
  geom_point(shape = 1, alpha = .7) +
  geom_smooth(method=lm, se=F) +
  theme_classic() + 
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE) +
  labs(color = "Age Group",
       x = "PROMIS PF 2.0 T-Score", y = "PROMIS PI T-Score", 
       title ="Correlation PROMIS Physical Functioning - Pain Interference",
       subtitle = "By Age Group",
       caption = "",
       alt = "") 
```


```{r}
cor(dataComplete$pf_tscore, dataComplete$pi_tscore,  method = "pearson", use = "complete.obs")

p <- ggscatter(dataComplete, x = "pf_tscore", y = "pi_tscore", 
          add = "reg.line", 
          add.params = list(color = "#5E81AC", fill = "lightgray"),
          conf.int = TRUE, 
          cor.method = "pearson",
          xlab = "PF 2.0 Custom SF", 
          ylab = "PI Custom SF",
          alpha = .7,
          ) + 
  stat_cor(p.accuracy = 0.001, r.accuracy = 0.01) 

ggMarginal(p, type="histogram", fill = "#D08770", xparams = list(  bins=20))
```

<br>

# Included items with item stems
```{r}
pf_items <- c("PFA1", 
              "PFA3", 
              "PFA5", 
              "PFA11", 
              "PFA12", 
              "PFA51", 
              "PFA56", 
              "PFB24", 
              "PFC12", 
              "PFC36r1", 
              "PFC37", 
              "PFC45r1", 
              "PFC46", 
              "PFM26", 
              "PFA14r1", 
              "PFA29r1", 
              "PFA34", 
              "PFA36", 
              "PFB13", 
              "PFB26", 
              "PFB28r1", 
              "PFB34")

ue_items <- c(
  "PFA14r1",
  "PFA29r1",
  "PFA34",
  "PFA36",
  "PFB13",
  "PFB26",
  "PFB28r1",
  "PFB34"
)

pi_items <- c(
  "PAININ3",
  "PAININ9",
  "PAININ12",
  "PAININ13",
  "PAININ22",
  "PAININ31",
  "PAININ34",
  "PAININ36")
```


#### PF Items
```{r}
pf_items_usa <- read_excel("data/raw/ao5_items.xlsx", sheet = 3) %>% 
  filter(variable %in% pf_items) %>% 
  select("Item Code" = variable, 
         "Item Stem" =  item) 

read_excel("data/raw/ao5_items.xlsx", sheet = 4) %>% 
  filter(Item %in% pf_items) %>% 
  select("Item Code" = Item, 
         "Item Stem" =  Itemtext) %>%
  bind_rows(pf_items_usa) %>% 
  dplyr::arrange(`Item Code`) %>% 
  tableHTML(.) %>% 
  write_tableHTML(., file = 'tables/pf_items.html')
```

#### UE Items
```{r}
ue_items_usa <- read_excel("data/raw/ao5_items.xlsx", sheet = 3) %>% 
  filter(variable %in% ue_items) %>% 
  select("Item Code" = variable, 
         "Item Stem" =  item)

read_excel("data/raw/ao5_items.xlsx", sheet = 4) %>% 
  filter(Item %in% ue_items) %>% 
  select("Item Code" = Item, 
         "Item Stem" =  Itemtext) %>% 
  bind_rows(ue_items_usa) %>% 
  dplyr::arrange(`Item Code`) %>% 
  tableHTML(.)
```

#### PI Items
```{r}
pi_items_usa <- read_excel("data/raw/ao5_items.xlsx", sheet = 3) %>% 
  filter(variable %in% pi_items) %>% 
  select("Item Code" = variable, 
         "Item Stem" =  item)

read_excel("data/raw/ao5_items.xlsx", sheet = 4) %>% 
  filter(Item %in% pi_items) %>% 
  select("Item Code" = Item,  
         "Item Stem" =  Itemtext) %>% 
    bind_rows(pi_items_usa) %>% 
  dplyr::arrange(`Item Code`) %>% 
  tableHTML(.) 
```

<br>

# Plausible Values
```{r}
sets_with_plausible_values <- readRDS("data/tidy/sets_with_plausible_values.rds")
```


## PF

```{r}
hist_pf_pv <- data.frame(mean = sets_with_plausible_values[[1]]$pf_pv,
         country = sets_with_plausible_values[[1]]$country_new ) %>% 
  ggplot(aes(x = sets_with_plausible_values[[1]]$pf_pv, fill = as.factor(country))) +
  geom_histogram(color="#e9ecef") +
  theme_bw() +
  ylab("") + 
  xlab("T-Score") +
  scale_fill_manual(values = met.brewer("Hokusai2",4)) +  
  theme(legend.position="none") +
  coord_cartesian(xlim = c(0,70)) +
  ggtitle("Plausible Values")


hist_pf <- dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_tscore, fill = Country)) +
  geom_histogram(color="#e9ecef") +
  theme_bw() +
  ylab("") + 
  xlab("T-Score") +
  scale_fill_manual(values = met.brewer("Hokusai2",4)) +  
  theme(legend.position="none") +
  coord_cartesian(xlim = c(0,70))  +
  ggtitle("Empirical Values")


hist_pf_sum <- dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pf_sum_score, fill = Country)) +
  geom_histogram(color="#e9ecef") +
  theme_bw() +
  ylab("") + 
  xlab("Sum Scores") +
  scale_fill_manual(values = met.brewer("Hokusai2",3)) +
  theme(legend.position="none") +
  ggtitle("Sum Scores")

text <- paste0("Empirical Values > 60 = ", round((nrow(filter(dataComplete, pf_tscore > 60)) / nrow(dataComplete))  * 100, 2), "%")

text_pf <- ggplot() + 
  annotate("text", x = 4, y = 25, size=5, label = text) + 
  theme_void()

pf <- plot_grid(hist_pf,
                text_pf,
                hist_pf_pv,
                hist_pf_sum,
                ncol = 2,
                align = "h",
                axis = "b")

title <- ggdraw() + 
  draw_label(
    "PROMIS Physical Functioning",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 40)
  )

pf <- plot_grid(
  title, pf,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)

pf 
```

### High PF
```{r}
pf_items <- c("PFA1", 
              "PFA3", 
              "PFA5", 
              "PFA11", 
              "PFA12", 
              "PFA51", 
              "PFA56", 
              "PFB24", 
              "PFC12", 
              "PFC36r1", 
              "PFC37", 
              "PFC45r1", 
              "PFC46", 
              "PFM26", 
              "PFA14r1", 
              "PFA29r1", 
              "PFA34", 
              "PFA36", 
              "PFB13", 
              "PFB26", 
              "PFB28r1", 
              "PFB34")

dataComplete %>% 
  filter(pf_tscore > 55) %>% 
  select(pf_tscore,
         ue_tscore, 
         pf_sum_score,
         pf_items
         )
```


```{r}
nrow(filter(dataComplete, pf_tscore > 60)) / nrow(dataComplete)
```

### Low PF
```{r}
dataComplete %>% 
  filter(pf_tscore < 30)  %>% 
  arrange(pf_tscore) %>% 
  select(pf_tscore,
         pf_sum_score,
         pf_items
  )
```

<br>

## UE
```{r}
hist_ue_pv <- data.frame(mean = sets_with_plausible_values[[1]]$ue_pv,
         country = sets_with_plausible_values[[1]]$country_new ) %>% 
  ggplot(aes(x = mean, fill = as.factor(country))) +
  geom_histogram() +
    theme_bw() +
  ylab("") + 
  xlab("T-Score") +
  scale_fill_nord("aurora") +
  theme(legend.position="none") +
  coord_cartesian(xlim = c(0,70)) +
  ggtitle("Plausible Values")


hist_ue <- dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = ue_tscore, fill = Country)) +
  geom_histogram() +
  theme_bw() +
  ylab("") + 
  xlab("T-Score") +
  scale_fill_nord("aurora") +
  theme(legend.position="none") +
  coord_cartesian(xlim = c(0,70))  +
  ggtitle("Empirical Values")


hist_ue_sum <- dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = ue_sum_score, fill = Country)) +
  geom_histogram(binwidth = 1) +
  theme_bw() +
  ylab("") + 
  xlab("Sum Scores") +
  scale_fill_nord("aurora") +
  theme(legend.position="none") +
  ggtitle("Sum Scores") 

text <- paste0("Empirical Values > 55 = ", round((nrow(filter(dataComplete, ue_tscore > 55)) / nrow(dataComplete))  * 100, 2), "%")


text_ue <- ggplot() + 
  annotate("text", x = 4, y = 25, size=5, label = text) + 
  theme_void()

ue <- plot_grid(hist_ue,
                text_ue,
                hist_ue_pv,
                hist_ue_sum,
                ncol = 2,
                align = "h",
                axis = "b")

title <- ggdraw() + 
  draw_label(
    "PROMIS Upper Extremities",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 40)
  )

ue <- plot_grid(
  title, ue,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
ue
```

```{r}
ue_items <- c(
  "PFA14r1",
  "PFA29r1",
  "PFA34",
  "PFA36",
  "PFB13",
  "PFB26",
  "PFB28r1",
  "PFB34"
)

dataComplete %>% 
  filter(ue_tscore > 55)  %>% 
  arrange(ue_tscore) %>% 
    select(ue_tscore,
         ue_sum_score,
         ue_items
         )

nrow(filter(dataComplete, ue_tscore > 55)) / nrow(dataComplete)
```




## PI
```{r}
hist_pi_pv <- data.frame(mean = sets_with_plausible_values[[1]]$pi_pv,
         country = sets_with_plausible_values[[1]]$country_new ) %>% 
  ggplot(aes(x = mean, fill = as.factor(country))) +
  geom_histogram() +
    theme_bw() +
  ylab("") + 
  xlab("T-Score") +
  scale_fill_nord("aurora") +
  theme(legend.position="none") +
  coord_cartesian(xlim = c(min(dataComplete$pi_tscore),80)) +
  ggtitle("Plausible Values")


hist_pi <- dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pi_tscore, fill = Country)) +
  geom_histogram() +
  theme_bw() +
  ylab("") + 
  xlab("T-Score") +
  scale_fill_nord("aurora") +
  theme(legend.position="none") +
  coord_cartesian(xlim = c(min(dataComplete$pi_tscore),80)) +
  ggtitle("Empirical Values")


hist_pi_sum <- dataComplete %>% 
  mutate(Country = country_table) %>% 
  ggplot(aes(x = pi_sum_score, fill = Country)) +
  geom_histogram() +
  theme_bw() +
  ylab("") + 
  xlab("Sum Scores") +
  scale_fill_nord("aurora") +
  theme(legend.position="none") +
  ggtitle("Sum Scores")


text <- paste0("Empirical Values < 41 = ", round((nrow(filter(dataComplete, pi_tscore < 41)) / nrow(dataComplete))  * 100, 2), "%")


text_pi <- ggplot() + 
  annotate("text", x = 4, y = 25, size=5, label = text) + 
  theme_void()

pi <- plot_grid(hist_pi,
                text_pi,
                hist_pi_pv,
                hist_pi_sum,
                ncol = 2,
                align = "h",
                axis = "b")
pi

title <- ggdraw() + 
  draw_label(
    "PROMIS Pain Interference",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 40)
  )

pi <- plot_grid(
  title, pi,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
pi
```

```{r}
pi_items <- c(
  "PAININ3",
  "PAININ9",
  "PAININ12",
  "PAININ13",
  "PAININ22",
  "PAININ31",
  "PAININ34",
  "PAININ36")

dataComplete %>% 
  filter(pi_tscore < 41)  %>% 
  arrange(pi_tscore) %>% 
    select(pi_tscore,
         pi_sum_score,
         pi_items
         )

nrow(filter(dataComplete, pi_tscore < 41)) / nrow(dataComplete)
```

```{r reproducibility_stuff, include=FALSE}
devtools::session_info() %>%
    yaml::write_yaml("code reproducibility/sessioninfo_5.yaml")
```