---
title: "Patient-Specific Reference Data for PROMIS PF, UE, & PI"
subtitle: "4. Median Regressions"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      encoding = encoding, 
      output_dir = "html") }) # print html in html folder
      rmarkdown::render(inputFile, 
output:
  html_document:
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: lumen
    toc: yes
    toc_depth: 3
    toc_float: yes
    numbersections: TRUE
editor_options: 
  chunk_output_type: console
---


```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(plyr)
library(tidyverse)
library(haven)
library(janitor)
library(labelled)
library(sjlabelled)
library(sjPlot)
library(summarytools)
library(lordif)
library(readxl)
library(mirt)
library(mirtCAT)
library(mitools) # multiple imputation
library(quantreg)
library(mitml) # multiple imputation
library(kableExtra)
library(reshape)
library(Amelia)
library(qwraps2) # summary statistics
library(kableExtra) # save html table
library(nord)
library(gghalves)
library(plotly)
library(viridis)
library(hrbrthemes)
library(svglite) # save svg
library(flextable)
library(skimr)
library(broom)
library(readxl)
library(effectsize)
```

# Overview

This document outlines all necessary steps for modeling regressions on country differences used for the publication on patient-specific reference values of PROMIS Physical Functioning items in the USA, UK, and Germany.

<br>

```{r warning=FALSE}
dataCompleteLatent <- readRDS("data/tidy/dataComplete.rds")
```


```{r}
dataCompleteLatent %>% 
  select(pf_tscore,
         ue_tscore,
         pi_tscore,
         country,
         age,
         sex) %>%
  skim()
```
<br>

## PF
```{r}
hist(dataCompleteLatent$pf_tscore)
qqnorm(dataCompleteLatent$pf_tscore)
qqline(dataCompleteLatent$pf_tscore)
```

<br>

### All countries
```{r}
dataCompleteLatent %>% 
  ggplot(aes(x = pf_tscore, color = country, fill = country)) +
geom_density(alpha=0.3) +
  facet_wrap(~agegroup, ncol = 1) +
  scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
      theme_ipsum() +
    theme(
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8))
```


## UE
```{r}
hist(dataCompleteLatent$ue_tscore)
qqnorm(dataCompleteLatent$ue_tscore)
qqline(dataCompleteLatent$ue_tscore)
```
```{r}
dataCompleteLatent %>% 
  ggplot(aes(x = ue_tscore, color = country, fill = country)) +
geom_density(alpha=0.3) +
  facet_wrap(~agegroup, ncol = 1) +
  scale_fill_viridis(discrete = TRUE) +
    scale_color_viridis(discrete = TRUE) +
      theme_ipsum() +
    theme(
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8))

ue_distribution_by_age_group <- dataCompleteLatent %>% 
  ggplot(aes(x = ue_tscore, color = country, fill = country)) +
  geom_histogram(alpha=0.3, position = "dodge") +
  facet_wrap(~agegroup, ncol = 1) +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_ipsum() +
  theme(
    panel.spacing = unit(0.1, "lines"),
    strip.text.x = element_text(size = 10)) 


dataCompleteLatent %>% 
  ggplot(aes(x = ue_tscore, color = country, fill = country)) +
  geom_histogram(alpha=0.3, position = "dodge") +
  scale_fill_viridis(discrete = TRUE) +
  scale_color_viridis(discrete = TRUE) +
  theme_ipsum() +
  theme(
    panel.spacing = unit(0.1, "lines"),
    strip.text.x = element_text(size = 10)) 


ue_distribution_by_age_group

```

<br>

## PI
```{r}
hist(dataCompleteLatent$pi_tscore)
qqnorm(dataCompleteLatent$pi_tscore)
qqline(dataCompleteLatent$pi_tscore)
```

```{r}
dataCompleteLatent %>% 
  ggplot(aes(x = pi_tscore, fill = country)) +
  geom_histogram(position = "dodge") +
  facet_wrap(~agegroup) +
  scale_fill_viridis(discrete = TRUE) +
  theme_minimal()
```

## PF


```{r}
dataCompleteLatent %>% 
  mutate(agegroup = as.factor(agegroup)) %>% 
  ggplot(aes(x = ue_tscore, color = country)) +
  geom_histogram() +
  facet_wrap(~agegroup) +
  theme_minimal()
```

## Model 1: Null-Model

### PF

#### LR
```{r}
lr_pf_1 <- lm("pf_tscore ~ 1", dataCompleteLatent)

summary(lr_pf_1)
confint(lr_pf_1)
```

#### QR
```{r}
qr_pf_1 <- quantreg::rq("pf_tscore ~ 1", 
                        data = dataCompleteLatent)
summary(qr_pf_1)
```

<br>

### UE

#### LR
```{r}
lr_ue_1 <- lm("ue_tscore ~ 1", dataCompleteLatent)

summary(lr_ue_1)
```

#### QR

```{r}
qr_ue_1 <- quantreg::rq("ue_tscore ~ 1", 
                        data = dataCompleteLatent)

summary(qr_ue_1)
```

### PI

#### LR
```{r}
lr_pi_1 <- lm("pi_tscore ~ 1", dataCompleteLatent)

summary(lr_pi_1)
```

#### QR
```{r}
qr_pi_1 <- rq("pi_tscore ~ 1", 
              data= dataCompleteLatent)

summary(qr_pi_1)
```

```{r}
# anova(lr_pf_country, lr_pf_country_age) # missings need to be removed
```



## Model 2: Country
```{r}
lr_pf_country <- lm("pf_tscore ~ country", dataCompleteLatent)

summary(lr_pf_country)
confint(lr_pf_country)
```


```{r}
lr_ue_country <- lm("ue_tscore ~ country", dataCompleteLatent)

summary(lr_ue_country)
confint(lr_ue_country)
```


```{r}
lr_pi_country <- lm("pi_tscore ~ country", dataCompleteLatent)

summary(lr_pi_country)
confint(lr_pi_country)
```

<br>

## Model 3: Country + Age
```{r}
lr_pf_country_age <- lm("pf_tscore ~ country + age", dataCompleteLatent)

summary(lr_pf_country_age)
confint(lr_pf_country_age)

lr_ue_country_age <- lm("ue_tscore ~ country + age", dataCompleteLatent)

summary(lr_ue_country_age)
confint(lr_ue_country_age)

lr_pi_country_age <- lm("pi_tscore ~ country + age", dataCompleteLatent)

summary(lr_pi_country_age)
confint(lr_pi_country_age)
```
<br>

## Model 4: `country` + `age` + `sex` 

### PF - With USA as Intercept

#### LR

```{r}
table(dataCompleteLatent$country)

str(dataCompleteLatent$country)

dataCompleteLatent$country <- factor(dataCompleteLatent$country, levels = c("usa", "ger", "uk"))
```

```{r}
lr_pf_country_age_sex <- lm("pf_tscore ~ country + age_50 + sex", dataCompleteLatent)

summary(lr_pf_country_age_sex)
confint(lr_pf_country_age_sex)
```

<br>

#### QR

```{r}
qr_pf_country_age_sex <- rq("pf_tscore ~ country + age_50 + sex", 
                            data = dataCompleteLatent, 
                            tau = .5)

summary(qr_pf_country_age_sex)
```

### PF - With Intercept

#### LR

```{r}
lr_pf_country_age_sex <- lm("pf_tscore ~ country + age_50 + sex", 
                            dataCompleteLatent)

summary(lr_pf_country_age_sex)
confint(lr_pf_country_age_sex)
```

<br>

#### QR

```{r}
qr_pf_country_age_sex <- rq("pf_tscore ~ country + age_50 + sex", 
                            data = dataCompleteLatent, 
                            tau = .5)

summary(qr_pf_country_age_sex)
```


<br>

#### Cohens´d

##### Germany - UK
```{r}
germany <- dataCompleteLatent %>% 
  filter(country_table == "Germany") %>% 
  select(germany_pf_tscore = pf_tscore) %>% 
  na.omit(germany_pf_tscore)

uk <- dataCompleteLatent %>% 
  filter(country_table == "UK") %>% 
  select(uk_pf_tscore = pf_tscore) %>% 
  na.omit(uk_pf_tscore)

bind_cols_fill <- function(df_list) {

  max_rows <- map_int(df_list, nrow) %>% max()
  
  map(df_list, function(df) {
    if(nrow(df) == max_rows) return(df)
    first <- names(df)[1] %>% sym()
    df %>% add_row(!!first := rep(NA, max_rows - nrow(df)))
  }) %>% bind_cols()
}

data_germany_uk <- bind_cols_fill(list(germany, uk))

cohens_d("germany_pf_tscore", "uk_pf_tscore", 
         data = data_germany_uk)

#rank_epsilon_squared(germany_pf_tscore ~ uk_pf_tscore, 
#         data = data_germany_uk)
```

<br>

##### Germany - USA
```{r}
germany <- dataCompleteLatent %>% 
  filter(country_table == "Germany") %>% 
  select(germany_pf_tscore = pf_tscore) %>% 
  na.omit(germany_pf_tscore)

usa <- dataCompleteLatent %>% 
  filter(country_table == "USA") %>% 
  select(usa_pf_tscore = pf_tscore) %>% 
  na.omit(usa_pf_tscore)

data_germany_usa <- bind_cols_fill(list(germany, usa))

cohens_d("germany_pf_tscore", "usa_pf_tscore", 
         data = data_germany_usa)
```

##### UK - USA


```{r}
data_uk_usa <- bind_cols_fill(list(usa, uk))

cohens_d("uk_pf_tscore", "usa_pf_tscore", 
         data = data_uk_usa)
```

#### Table

https://lachlandeer.github.io/post/quantile-regression-with-tidyverse/ 

```{r}
quants <- c(0.25, 0.5, 0.75)

lr_pf_country_age_sex <- lm("pf_tscore ~ country + age_50 + sex", dataCompleteLatent)

qr_pf <- map(quants, ~rq("pf_tscore ~ country + age_50 + sex", 
                         data = dataCompleteLatent, 
                         tau = .x)
)

stargazer::stargazer(lr_pf_country_age_sex, qr_pf, 
                     order = c(5, 1, 2, 3, 4),
                     rq.se = "boot",
                     ci = TRUE,
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("Intercept (USA)",
                                          "Germany",
                                          "UK",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Physical Functioning 2.0",
                     #omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_pf_table_intercept.html"
                     )
```



<br>

#### Plot

```{r}
qr_pf_tidy <- map(qr_pf, ~broom::tidy(.x, se = "boot",
                                      conf.int = T)) %>%
            bind_rows()

ols_tidy <- tidy(lr_pf_country_age_sex)

country_difference_pf_plot <- qr_pf_tidy %>%
  ggplot(aes(x = tau,
             y = estimate
             )
         ) + # the data we want to plot - in our case the tidied quantile regression output
  geom_point(color = "#27408b", 
             size = 3
             ) + # plots the coefficient estimates
  geom_line(color="#27408b", 
            size = 1
            ) + # adds a line connecting the coefficient estimates
  geom_errorbar(aes(
    ymin = conf.low,
    ymax = conf.high
      ), 
    width = 0.05,
    size  = 0.3,
    position = position_dodge(.9)
    ) + # adds the confidence intervals as error bars
  geom_hline(data = ols_tidy, 
             aes(yintercept = estimate), 
             color = "red"
             ) + # add OLS estimate - note it is from another data set which is totally OK
  facet_wrap(~term, 
             scales="free", 
             ncol=2
             ) + # one plot per explanatory variable, subplots over 2 columns
  theme_minimal()

country_difference_pf_plot
```

### PF - Without Intercept

#### LR

```{r}
lr_pf_country_age_sex <- lm("pf_tscore ~ country + age_50 + sex - 1", dataCompleteLatent)

summary(lr_pf_country_age_sex)
confint(lr_pf_country_age_sex)
```

<br>

#### QR

```{r}
qr_pf_country_age_sex <- rq("pf_tscore ~ country + age_50 + sex - 1", 
                            data = dataCompleteLatent, 
                            tau = .5)

summary(qr_pf_country_age_sex)
```


<br>


#### Table

https://lachlandeer.github.io/post/quantile-regression-with-tidyverse/ 

```{r}
quants <- c(0.25, 0.5, 0.75)

lr_pf_country_age_sex <- lm("pf_tscore ~ country + age_50 + sex -1", dataCompleteLatent)

qr_pf <- map(quants, ~rq("pf_tscore ~ country + age_50 + sex -1", 
                         data = dataCompleteLatent, 
                         tau = .x)
)

stargazer::stargazer(lr_pf_country_age_sex, qr_pf, 
                     rq.se = "boot",
                     ci = TRUE,
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("USA",
                                          "Germany",
                                          "UK",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Physical Functioning 2.0",
                     #omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_pf_table.html"
                     )
```

<br>

#### Plot

```{r}
qr_pf_tidy <- map(qr_pf, ~broom::tidy(.x, se = "boot",
                                      conf.int = T)) %>%
            bind_rows()

ols_tidy <- tidy(lr_pf_country_age_sex)

country_difference_pf_plot <- qr_pf_tidy %>%
  ggplot(aes(x = tau,
             y = estimate
             )
         ) + # the data we want to plot - in our case the tidied quantile regression output
  geom_point(color = "#27408b", 
             size = 3
             ) + # plots the coefficient estimates
  geom_line(color="#27408b", 
            size = 1
            ) + # adds a line connecting the coefficient estimates
  geom_errorbar(aes(
    ymin = conf.low,
    ymax = conf.high
      ), 
    width = 0.05,
    size  = 0.3,
    position = position_dodge(.9)
    ) + # adds the confidence intervals as error bars
  geom_hline(data = ols_tidy, 
             aes(yintercept = estimate), 
             color = "red"
             ) + # add OLS estimate - note it is from another data set which is totally OK
  facet_wrap(~term, 
             scales="free", 
             ncol=2
             ) + # one plot per explanatory variable, subplots over 2 columns
  theme_minimal()

country_difference_pf_plot
```

<br>

### UE - With Intercept

#### LR

```{r}
lr_ue_country_age_sex <- lm("ue_tscore ~ country + age + sex", dataCompleteLatent)

summary(lr_ue_country_age_sex)
confint(lr_ue_country_age_sex)
```

#### QR

```{r}
qr_ue_country_age_sex <- rq("ue_tscore ~ country + age_50 + sex", 
                            data = dataCompleteLatent)

summary(qr_ue_country_age_sex)
```

#### Table

```{r}
quants <- .5

qr_ue <- map(quants, ~rq("ue_tscore ~ country + age_50 + sex", 
                         data = dataCompleteLatent, 
                         tau = .x))

lr_ue_country_age_sex <- lm("ue_tscore ~ country + age_50 + sex", 
                            dataCompleteLatent)

stargazer::stargazer(lr_ue_country_age_sex, 
                     qr_ue, 
                     rq.se = "boot",
                     order = c(5,1,2,3,4),
                     ci = TRUE,
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("Intercept (USA)",
                                          "Germany",
                                          "UK",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Upper Extremities 2.0",
                     # omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_ue_table_intercept.txt")

stargazer::stargazer(lr_ue_country_age_sex, 
                     qr_ue, 
                     order = c(5,1,2,3,4),
                     
                     rq.se = "boot",
                     ci = TRUE,
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("Intercept (USA)",
                                          "Germany",
                                          "UK",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Upper Extremities 2.0",
                     #omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_ue_table_intercept.html")
```

#### Cohens´d

##### Germany - UK
```{r}
germany_ue <- dataCompleteLatent %>% 
  filter(country_table == "Germany") %>% 
  select(germany_ue_tscore = ue_tscore) %>% 
  na.omit(germany_ue_tscore)

uk_ue <- dataCompleteLatent %>% 
  filter(country_table == "UK") %>% 
  select(uk_ue_tscore = ue_tscore) %>% 
  na.omit(uk_ue_tscore)

bind_cols_fill <- function(df_list) {

  max_rows <- map_int(df_list, nrow) %>% max()
  
  map(df_list, function(df) {
    if(nrow(df) == max_rows) return(df)
    first <- names(df)[1] %>% sym()
    df %>% add_row(!!first := rep(NA, max_rows - nrow(df)))
  }) %>% bind_cols()
}

data_germany_uk_ue <- bind_cols_fill(list(germany_ue, uk_ue))

cohens_d("germany_ue_tscore", "uk_ue_tscore", 
         data = data_germany_uk_ue)

```

<br>

das kann nicht stimmen!!!
##### Germany - USA
```{r}
usa_ue <- dataCompleteLatent %>% 
  filter(country_table == "USA") %>% 
  select(usa_ue_tscore = ue_tscore) %>% 
  na.omit(usa_ue_tscore)

data_germany_usa_ue <- bind_cols_fill(list(germany_ue, usa_ue))

cohens_d("germany_ue_tscore", "usa_ue_tscore", 
         data = data_germany_usa_ue)
```

##### UK - USA
```{r}
data_uk_usa_ue <- bind_cols_fill(list(uk_ue, usa_ue))

cohens_d("uk_ue_tscore", "usa_ue_tscore", 
         data = data_uk_usa_ue)
```

### UE - Without Intercept

#### Table

```{r}
quants <- .5

qr_ue <- map(quants, ~rq("ue_tscore ~ country + age_50 + sex - 1", 
                         data = dataCompleteLatent, 
                         tau = .x))

lr_ue_country_age_sex <- lm("ue_tscore ~ country + age_50 + sex - 1", 
                            dataCompleteLatent)

stargazer::stargazer(lr_ue_country_age_sex, 
                     qr_ue, 
                     rq.se = "boot",
                     ci = TRUE,
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("Germany",
                                          "UK",
                                          "USA",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Upper Extremities 2.0",
                     omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_ue_table.html")
```

https://stats.stackexchange.com/questions/78022/cause-of-singularity-in-matrix-for-quantile-regression 

<br>

#### Plot


ci?
```{r}
qr_ue_tidy <- map(qr_ue, ~broom::tidy(.x, se = "boot",
                                      conf.int = T)) %>%
            bind_rows()

ols_tidy <- tidy(lr_ue_country_age_sex)

country_difference_ue_plot <- qr_ue_tidy %>%
  ggplot(aes(x = tau,
             y = estimate
             )
         ) + # the data we want to plot - in our case the tidied quantile regression output
  geom_point(color = "#27408b", 
             size = 3
             ) + # plots the coefficient estimates
  geom_line(color="#27408b", 
            size = 1
            ) + # adds a line connecting the coefficient estimates
  geom_errorbar(aes(
    ymin = conf.low,
    ymax = conf.high
      ), 
    width = 0.05,
    size  = 0.3,
    position = position_dodge(.9)
    ) + # adds the confidence intervals as error bars
  geom_hline(data = ols_tidy, 
             aes(yintercept = estimate), 
             color = "red"
             ) + # add OLS estimate - note it is from another data set which is totally OK
  facet_wrap(~term, 
             scales="free", 
             ncol=2
             ) + # one plot per explanatory variable, subplots over 2 columns
  theme_minimal()

country_difference_ue_plot
```

<br>

### PI - With intercept

#### QR


#### Cohens´d

##### Germany - UK
```{r}
germany_pi <- dataCompleteLatent %>% 
  filter(country_table == "Germany") %>% 
  select(germany_pi_tscore = pi_tscore) %>% 
  na.omit(germany_pi_tscore)

uk_pi <- dataCompleteLatent %>% 
  filter(country_table == "UK") %>% 
  select(uk_pi_tscore = pi_tscore) %>% 
  na.omit(uk_pi_tscore)

bind_cols_fill <- function(df_list) {

  max_rows <- map_int(df_list, nrow) %>% max()
  
  map(df_list, function(df) {
    if(nrow(df) == max_rows) return(df)
    first <- names(df)[1] %>% sym()
    df %>% add_row(!!first := rep(NA, max_rows - nrow(df)))
  }) %>% bind_cols()
}

data_germany_uk_pi <- bind_cols_fill(list(germany_pi, uk_pi))

cohens_d("germany_pi_tscore", "uk_pi_tscore", 
         data = data_germany_uk_pi)

```

<br>


##### Germany - USA
```{r}
usa_pi <- dataCompleteLatent %>% 
  filter(country_table == "USA") %>% 
  select(usa_pi_tscore = pi_tscore) %>% 
  na.omit(usa_pi_tscore)

data_germany_usa_pi <- bind_cols_fill(list(germany_pi, usa_pi))

cohens_d("germany_pi_tscore", "usa_pi_tscore", 
         data = data_germany_usa_pi)
```

##### UK - USA
```{r}
data_uk_usa_pi <- bind_cols_fill(list(uk_pi, usa_pi))

cohens_d("uk_pi_tscore", "usa_pi_tscore", 
         data = data_uk_usa_pi)
```


***

#### LR

```{r}
lr_pi_country_age_sex <- lm("pi_tscore ~ country + age + sex", dataCompleteLatent)

summary(lr_pi_country_age_sex)
```

#### QR

```{r}
qr_pi_country_age_sex <- rq("pi_tscore ~ country + age_50 + sex", 
                            data = dataCompleteLatent)

summary(qr_pi_country_age_sex)
```


#### Table

```{r}
quants <- .5

qr_pi <- map(quants, ~rq("pi_tscore ~ country + age_50 + sex", 
                         data = dataCompleteLatent, 
                         tau = .x))

lr_pi_country_age_sex <- lm("pi_tscore ~ country + age_50 + sex", 
                            dataCompleteLatent)

stargazer::stargazer(lr_pi_country_age_sex, 
                     qr_pi, 
                     rq.se = "boot",
                     ci = TRUE,
                     order = c(5,1,2,3,4),
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("Intercept (USA)",
                                          "Germany",
                                          "UK",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Pain Interference",
                     #omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     #keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_pi_table_intercept.html")
```

https://stats.stackexchange.com/qpistions/78022/cause-of-singularity-in-matrix-for-quantile-regression 

<br>

#### Plot

```{r}
#tidy(qr_pi[[2]], se = "boot")
```


```{r}
qr_pi_tidy <- map(qr_pi, ~broom::tidy(.x, se = "boot",
                                      conf.int = T)) %>%
            bind_rows()

ols_tidy <- tidy(lr_pi_country_age_sex)


country_difference_pi_plot <- qr_pi_tidy %>%
  ggplot(aes(x = tau,
             y = estimate
             )
         ) + # the data we want to plot - in our case the tidied quantile regression output
  geom_point(color = "#27408b", 
             size = 3
             ) + # plots the coefficient estimates
  geom_line(color="#27408b", 
            size = 1
            ) + # adds a line connecting the coefficient estimates
  geom_errorbar(aes(
    ymin = conf.low,
    ymax = conf.high
      ), 
    width = 0.05,
    size  = 0.3,
    position = position_dodge(.9)
    ) + # adds the confidence intervals as error bars
  geom_hline(data = ols_tidy, 
             aes(yintercept = estimate), 
             color = "red"
             ) + # add OLS estimate - note it is from another data set which is totally OK
  facet_wrap(~term, 
             scales="free", 
             ncol=2
             ) + # one plot per explanatory variable, subplots over 2 columns
  theme_minimal()

country_difference_pi_plot
```

### PI - Without Intercept

#### LR

```{r}
lr_pi_country_age_sex <- lm("pi_tscore ~ country + age + sex", dataCompleteLatent)

summary(lr_pi_country_age_sex)
```

#### QR

```{r}
qr_pi_country_age_sex <- rq("pi_tscore ~ country + age_50 + sex - 1", 
                            data = dataCompleteLatent)

summary(qr_pi_country_age_sex)
```


#### Table

```{r}
quants <- .5

qr_pi <- map(quants, ~rq("pi_tscore ~ country + age_50 + sex - 1", 
                         data = dataCompleteLatent, 
                         tau = .x))

lr_pi_country_age_sex <- lm("pi_tscore ~ country + age_50 + sex - 1", 
                            dataCompleteLatent)


stargazer::stargazer(lr_pi_country_age_sex, 
                     qr_pi, 
                     rq.se = "boot",
                     ci = TRUE,
                     column.labels = c("OLS", paste("tau = ", quants)),
                     covariate.labels = c("Germany",
                                          "UK",
                                          "USA",
                                          "Age",
                                          "Sex"),
                     dep.var.labels = "PROMIS Pain Interference",
                     omit = c("Constant"),
                     model.numbers = TRUE,
                     model.names =  FALSE,
                     #keep.stat = c('n'),
                     type ='text',
                     out = "tables/country_comparison_pi_table.html")
```

https://stats.stackexchange.com/qpistions/78022/cause-of-singularity-in-matrix-for-quantile-regression 

<br>

#### Plot

```{r}
qr_pi_tidy <- map(qr_pi, ~broom::tidy(.x, se = "boot",
                                      conf.int = T)) %>%
            bind_rows()

ols_tidy <- tidy(lr_pi_country_age_sex)


country_difference_pi_plot <- qr_pi_tidy %>%
  ggplot(aes(x = tau,
             y = estimate
             )
         ) + # the data we want to plot - in our case the tidied quantile regression output
  geom_point(color = "#27408b", 
             size = 3
             ) + # plots the coefficient estimates
  geom_line(color="#27408b", 
            size = 1
            ) + # adds a line connecting the coefficient estimates
  geom_errorbar(aes(
    ymin = conf.low,
    ymax = conf.high
      ), 
    width = 0.05,
    size  = 0.3,
    position = position_dodge(.9)
    ) + # adds the confidence intervals as error bars
  geom_hline(data = ols_tidy, 
             aes(yintercept = estimate), 
             color = "red"
             ) + # add OLS estimate - note it is from another data set which is totally OK
  facet_wrap(~term, 
             scales="free", 
             ncol=2
             ) + # one plot per explanatory variable, subplots over 2 columns
  theme_minimal()

country_difference_pi_plot
```


```{r reproducibility_stuff}
devtools::session_info() %>%
    yaml::write_yaml("code reproducibility/sessioninfo_4.yaml")
```