---
title: "Patient-Specific Reference Data for PROMIS PF, UE, & PI"
subtitle: "2.1 Quantile Regression: Model Selection"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      encoding = encoding, 
      output_dir = "html") })
      rmarkdown::render(inputFile, 
output:
  html_document:
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
    numbersections: TRUE
editor_options: 
  chunk_output_type: console
---



```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(plyr)
library(tidyverse)
library(haven)
library(janitor)
library(labelled)
library(sjlabelled)
library(sjPlot)
library(summarytools)
library(lordif)
library(readxl)
library(mirt)
library(mirtCAT)
library(mitools) # multiple imputation
library(quantreg)
library(mitml) # multiple imputation
library(kableExtra)
library(reshape)
library(Amelia)
library(qwraps2) # summary statistics
library(kableExtra) # save html table
library(nord)
library(gghalves)
library(plotly)
library(viridis)
library(svglite) # save svg
library(flextable)
```

# About

This document outlines all necessary steps for visualizing the model fit and following model selection for the publication on patient-specific reference values of PROMIS Physical Functioning items in the USA, UK, and Germany.

# Load data

```{r, warning=FALSE}
models <- readRDS("data/tidy/models_age_50.rds") 
```

<br>

# Model Selection

## PF

```{r}
mod_comparison <- cbind(models$pf_pv$AIC$formula_0,
                        models$pf_pv$AIC$formula_1,
                        models$pf_pv$AIC$formula_2,
                        models$pf_pv$AIC$formula_3,
                        models$pf_pv$AIC$formula_4,
                        models$pf_pv$AIC$formula_5,
                        models$pf_pv$AIC$formula_6,
                        models$pf_pv$AIC$formula_7)

colnames(mod_comparison) <- c("id", "tau", 
                              "Model 0: AIC", "Model 0: BIC", "delete", "delete", 
                              "Model 1: AIC", "Model 1: BIC", "delete", "delete", 
                              "Model 2: AIC", "Model 2: BIC", "delete", "delete", 
                              "Model 3: AIC", "Model 3: BIC", "delete", "delete", 
                              "Model 4: AIC", "Model 4: BIC", "delete", "delete", 
                              "Model 5: AIC", "Model 5: BIC", "delete", "delete", 
                              "Model 6: AIC", "Model 6: BIC", "delete", "delete", 
                              "Model 7: AIC", "Model 7: BIC" )

mod_comparison_clean <- mod_comparison %>% 
  select(-delete) %>%
  pivot_longer(cols = "Model 0: AIC":"Model 7: BIC",
               names_to = "model") %>% 
    mutate(model = as.factor(model),
           criterion = ifelse(str_detect(model, "AIC"), "AIC", "BIC"),
           model = str_replace(model, (":.*"), ""))
```

<br>

### Plot AIC by quantile
```{r}
p1_pf <- mod_comparison_clean %>% 
  filter(criterion == "AIC") %>% 
  ggplot(aes(x = model, y = value, color = model)) +
  geom_boxplot() +
  geom_jitter(alpha = .3) +
  facet_wrap(~ tau, scales = "free") +
  theme_minimal() +
  #theme(legend.position = "none") +
  labs(x = "Model",
       y = "AIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PF ~ 1"),
                                   paste("Model 1: PF ~ age_50"),
                                   paste("Model 2: PF ~ age_50 + sex"),
                                   paste("Model 3: PF ~ age_50 + country"),
                                   paste("Model 4: PF ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PF ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PF ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PF ~ age_50 * sex * country")))   +
  theme(legend.position = c(1, 0),
        legend.justification = c(1, 0))

p1_pf

ggsave(p1_pf, filename = "figures/model_fit_PF_AIC_by_quantile.svg", width = 20, height = 15, dpi = "retina")
```

<br>


### Plot AIC

```{r}
p2_pf <- mod_comparison_clean %>% 
  ggplot(aes(x = as.factor(tau), y = value, color = model)) +
  geom_boxplot() +
  theme_minimal() + 
  # theme(legend.position = "none") +
  labs(x = "Quantiles",
       y = "AIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PF ~ 1"),
                                   paste("Model 1: PF ~ age_50"),
                                   paste("Model 2: PF ~ age_50 + sex"),
                                   paste("Model 3: PF ~ age_50 + country"),
                                   paste("Model 4: PF ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PF ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PF ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PF ~ age_50 * sex * country"))) 

p2_pf

ggsave(p2_pf, filename = "figures/model_fit_PF_AIC.svg", width = 20, height = 15, dpi = "retina")
```

<br>

### Plot BIC by quantile
```{r}
p3_pf <- mod_comparison_clean %>% 
  filter(criterion == "BIC") %>% 
  ggplot(aes(x = model, y = value, color = model)) +
  geom_boxplot() +
  geom_jitter(alpha = .3) +
  facet_wrap(~ tau, scales = "free") +
  theme_minimal() +
  #theme(legend.position = "none") +
  labs(x = "Model",
       y = "BIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PF ~ 1"),
                                   paste("Model 1: PF ~ age_50"),
                                   paste("Model 2: PF ~ age_50 + sex"),
                                   paste("Model 3: PF ~ age_50 + country"),
                                   paste("Model 4: PF ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PF ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PF ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PF ~ age_50 * sex * country")))   +
  theme(legend.position = c(1, 0),
        legend.justification = c(1, 0))

p3_pf

ggsave(p3_pf, filename = "figures/model_fit_PF_BIC_by_quantile.svg", width = 20, height = 15, dpi = "retina")
```

<br>

### Plot BIC

```{r}
p4_pf <- mod_comparison_clean %>% 
  ggplot(aes(x = as.factor(tau), y = value, color = model)) +
  geom_boxplot() +
  theme_minimal() + 
  # theme(legend.position = "none") +
  labs(x = "Quantiles",
       y = "BIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PF ~ 1"),
                                   paste("Model 1: PF ~ age_50"),
                                   paste("Model 2: PF ~ age_50 + sex"),
                                   paste("Model 3: PF ~ age_50 + country"),
                                   paste("Model 4: PF ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PF ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PF ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PF ~ age_50 * sex * country")))   

p4_pf

ggsave(p4_pf, filename = "figures/model_fit_PF_BIC.svg", width = 20, height = 15, dpi = "retina")
```

<br>

## UE

```{r}
mod_comparison_ue <- cbind(models$ue_pv$AIC$formula_0,
                           models$ue_pv$AIC$formula_1,
                           models$ue_pv$AIC$formula_2,
                           models$ue_pv$AIC$formula_3,
                           models$ue_pv$AIC$formula_4,
                           models$ue_pv$AIC$formula_5,
                           models$ue_pv$AIC$formula_6,
                           models$ue_pv$AIC$formula_7)


colnames(mod_comparison_ue) <- c("id", "tau", 
                              "Model 0: AIC", "Model 0: BIC", "delete", "delete", 
                              "Model 1: AIC", "Model 1: BIC", "delete", "delete", 
                              "Model 2: AIC", "Model 2: BIC", "delete", "delete", 
                              "Model 3: AIC", "Model 3: BIC", "delete", "delete", 
                              "Model 4: AIC", "Model 4: BIC", "delete", "delete", 
                              "Model 5: AIC", "Model 5: BIC", "delete", "delete", 
                              "Model 6: AIC", "Model 6: BIC", "delete", "delete", 
                              "Model 7: AIC", "Model 7: BIC" )

mod_comparison_ue_clean <- mod_comparison_ue %>% 
  select(-delete) %>%
  pivot_longer(cols = "Model 0: AIC":"Model 7: BIC",
               names_to = "model") %>% 
    mutate(model = as.factor(model),
           criterion = ifelse(str_detect(model, "AIC"), "AIC", "BIC"),
           model = str_replace(model, (":.*"), ""))
```

<br>

### Plot AIC by quantile
```{r}
p1_ue <- mod_comparison_ue_clean %>% 
  filter(criterion == "AIC") %>% 
  ggplot(aes(x = model, y = value, color = model)) +
  geom_boxplot() +
  geom_jitter(alpha = .3) +
  facet_wrap(~ tau, scales = "free") +
  theme_minimal() +
  #theme(legend.position = "none") +
  labs(x = "Model",
       y = "AIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: UE ~ 1"),
                                   paste("Model 1: UE ~ age_50"),
                                   paste("Model 2: UE ~ age_50 + sex"),
                                   paste("Model 3: UE ~ age_50 + country"),
                                   paste("Model 4: UE ~ age_50 + sex + country - 1"),
                                   paste("Model 5: UE ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: UE ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: UE ~ age_50 * sex * country")))   +
  theme(legend.position = c(1, 0),
        legend.justification = c(1, 0))
p1_ue

ggsave(p1_ue, filename = "figures/model_fit_ue_AIC_by_quantile.svg", width = 20, height = 15, dpi = "retina")
```

<br>


### Plot AIC

```{r}
p2_ue <- mod_comparison_ue_clean %>% 
  ggplot(aes(x = as.factor(tau), y = value, color = model)) +
  geom_boxplot() +
  theme_minimal() + 
  # theme(legend.position = "none") +
  labs(x = "Quantiles",
       y = "AIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: UE ~ 1"),
                                   paste("Model 1: UE ~ age_50"),
                                   paste("Model 2: UE ~ age_50 + sex"),
                                   paste("Model 3: UE ~ age_50 + country"),
                                   paste("Model 4: UE ~ age_50 + sex + country - 1"),
                                   paste("Model 5: UE ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: UE ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: UE ~ age_50 * sex * country"))) 

p2_ue

ggsave(p2_ue, filename = "figures/model_fit_ue_AIC.svg", width = 20, height = 15, dpi = "retina")
```

<br>

### Plot BIC by quantile
```{r}
p3_ue <- mod_comparison_ue_clean %>% 
  filter(criterion == "BIC") %>% 
  ggplot(aes(x = model, y = value, color = model)) +
  geom_boxplot() +
  geom_jitter(alpha = .3) +
  facet_wrap(~ tau, scales = "free") +
  theme_minimal() +
  #theme(legend.position = "none") +
  labs(x = "Model",
       y = "BIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: UE ~ 1"),
                                   paste("Model 1: UE ~ age_50"),
                                   paste("Model 2: UE ~ age_50 + sex"),
                                   paste("Model 3: UE ~ age_50 + country"),
                                   paste("Model 4: UE ~ age_50 + sex + country - 1"),
                                   paste("Model 5: UE ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: UE ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: UE ~ age_50 * sex * country")))   +
  theme(legend.position = c(1, 0),
        legend.justification = c(1, 0))

p3_ue

ggsave(p3_ue, filename = "figures/model_fit_ue_BIC_by_quantile.svg", width = 20, height = 15, dpi = "retina")
```

<br>

### Plot BIC

```{r}
p4_ue <- mod_comparison_ue_clean %>% 
  ggplot(aes(x = as.factor(tau), y = value, color = model)) +
  geom_boxplot() +
  theme_minimal() + 
  # theme(legend.position = "none") +
  labs(x = "Quantiles",
       y = "BIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: UE ~ 1"),
                                   paste("Model 1: UE ~ age_50"),
                                   paste("Model 2: UE ~ age_50 + sex"),
                                   paste("Model 3: UE ~ age_50 + country"),
                                   paste("Model 4: UE ~ age_50 + sex + country - 1"),
                                   paste("Model 5: UE ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: UE ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: UE ~ age_50 * sex * country"))) 

p4_ue

ggsave(p4_ue, filename = "figures/model_fit_ue_BIC.svg", width = 20, height = 15, dpi = "retina")
```

<br>

## PI

```{r}
mod_comparison_pi <- cbind(models$pi_pv$AIC$formula_0,
                           models$pi_pv$AIC$formula_1,
                           models$pi_pv$AIC$formula_2,
                           models$pi_pv$AIC$formula_3,
                           models$pi_pv$AIC$formula_4,
                           models$pi_pv$AIC$formula_5,
                           models$pi_pv$AIC$formula_6,
                           models$pi_pv$AIC$formula_7)


colnames(mod_comparison_pi) <- c("id", "tau", 
                              "Model 0: AIC", "Model 0: BIC", "delete", "delete", 
                              "Model 1: AIC", "Model 1: BIC", "delete", "delete", 
                              "Model 2: AIC", "Model 2: BIC", "delete", "delete", 
                              "Model 3: AIC", "Model 3: BIC", "delete", "delete", 
                              "Model 4: AIC", "Model 4: BIC", "delete", "delete", 
                              "Model 5: AIC", "Model 5: BIC", "delete", "delete", 
                              "Model 6: AIC", "Model 6: BIC", "delete", "delete", 
                              "Model 7: AIC", "Model 7: BIC" )

mod_comparison_pi_clean <- mod_comparison_pi %>% 
  select(-delete) %>%
  pivot_longer(cols = "Model 0: AIC":"Model 7: BIC",
               names_to = "model") %>% 
    mutate(model = as.factor(model),
           criterion = ifelse(str_detect(model, "AIC"), "AIC", "BIC"),
           model = str_replace(model, (":.*"), ""))
```

<br>

### Plot AIC by quantile
```{r}
p1_pi <- mod_comparison_pi_clean %>% 
  filter(criterion == "AIC") %>% 
  ggplot(aes(x = model, y = value, color = model)) +
  geom_boxplot() +
  geom_jitter(alpha = .3) +
  facet_wrap(~ tau, scales = "free") +
  theme_minimal() +
  #theme(legend.position = "none") +
  labs(x = "Model",
       y = "AIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PI ~ 1"),
                                   paste("Model 1: PI ~ age_50"),
                                   paste("Model 2: PI ~ age_50 + sex"),
                                   paste("Model 3: PI ~ age_50 + country"),
                                   paste("Model 4: PI ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PI ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PI ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PI ~ age_50 * sex * country")))   +
  theme(legend.position = c(1, 0),
        legend.justification = c(1, 0))
p1_pi
ggsave(p1_pi, filename = "figures/model_fit_pi_AIC_by_quantile.svg", width = 20, height = 15, dpi = "retina")
```

<br>


### Plot AIC

```{r}
p2_pi <- mod_comparison_pi_clean %>% 
  ggplot(aes(x = as.factor(tau), y = value, color = model)) +
  geom_boxplot() +
  theme_minimal() + 
  # theme(legend.position = "none") +
  labs(x = "Quantiles",
       y = "AIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PI ~ 1"),
                                   paste("Model 1: PI ~ age_50"),
                                   paste("Model 2: PI ~ age_50 + sex"),
                                   paste("Model 3: PI ~ age_50 + country"),
                                   paste("Model 4: PI ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PI ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PI ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PI ~ age_50 * sex * country")))

p2_pi

ggsave(p2_pi, filename = "figures/model_fit_pi_AIC.svg", width = 20, height = 15, dpi = "retina")
```

<br>

### Plot BIC by quantile
```{r}
p3_pi <- mod_comparison_pi_clean %>% 
  filter(criterion == "BIC") %>% 
  ggplot(aes(x = model, y = value, color = model)) +
  geom_boxplot() +
  geom_jitter(alpha = .3) +
  facet_wrap(~ tau, scales = "free") +
  theme_minimal() +
  #theme(legend.position = "none") +
  labs(x = "Model",
       y = "BIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PI ~ 1"),
                                   paste("Model 1: PI ~ age_50"),
                                   paste("Model 2: PI ~ age_50 + sex"),
                                   paste("Model 3: PI ~ age_50 + country"),
                                   paste("Model 4: PI ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PI ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PI ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PI ~ age_50 * sex * country")))  +
  theme(legend.position = c(1, 0),
        legend.justification = c(1, 0))

p3_pi

ggsave(p3_pi, filename = "figures/model_fit_pi_BIC_by_quantile.svg", width = 20, height = 15, dpi = "retina")
```

<br>

### Plot BIC

```{r}
p4_pi <- mod_comparison_pi_clean %>% 
  ggplot(aes(x = as.factor(tau), y = value, color = model)) +
  geom_boxplot() +
  theme_minimal() + 
  # theme(legend.position = "none") +
  labs(x = "Quantiles",
       y = "BIC") +
  scale_color_viridis_d(labels = c(paste("Model 0: PI ~ 1"),
                                   paste("Model 1: PI ~ age_50"),
                                   paste("Model 2: PI ~ age_50 + sex"),
                                   paste("Model 3: PI ~ age_50 + country"),
                                   paste("Model 4: PI ~ age_50 + sex + country - 1"),
                                   paste("Model 5: PI ~ age_50 + I(age_50^2) + country + sex -1"),
                                   paste("Model 6: PI ~ age_50 + sex + country + country:sex + country:age_50"),
                                   paste("Model 7: PI ~ age_50 * sex * country")))

p4_pi

ggsave(p4_pi, filename = "figures/model_fit_pi_BIC.svg", width = 20, height = 15, dpi = "retina")
```


## Summary Model Fit

Based on the above findings we decide to use model 4 for all domains, as the fit does not improve substantially with adding more complexity beyond the additive model 4.

<br>

```{r reproducibility_stuff, include=FALSE}
devtools::session_info() %>%
    yaml::write_yaml("code reproducibility/sessioninfo_2.1.yaml")
```
