---
title: "Patient-Specific Reference Data for PROMIS PF, UE, & PI"
subtitle: "2. Quantile Regression"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile, 
      encoding = encoding, 
      output_dir = "html") })
output:
  html_document:
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: cerulean
    toc: yes
    toc_depth: 3
    toc_float: yes
    numbersections: TRUE
editor_options: 
  chunk_output_type: inline
---



```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(plyr)
library(tidyverse)
library(haven)
library(janitor)
library(labelled)
library(sjlabelled)
library(sjPlot)
library(summarytools)
library(lordif)
library(readxl)
library(mirt)
library(mirtCAT)
library(mitools) # multiple imputation
library(quantreg)
library(mitml) # multiple imputation
library(kableExtra)
library(reshape)
library(Amelia)
library(qwraps2) # summary statistics
library(kableExtra) # save html table
library(nord)
library(gghalves)
library(plotly)
library(viridis)
library(svglite) # save svg
library(flextable)
```

# About

This document outlines all necessary steps for calculating the quantile regressions for the publication on patient-specific reference values of PROMIS Physical Functioning items in the USA, UK, and Germany.

# Load Data

```{r, warning=FALSE}
sets_with_plausible_values <- readRDS("data/tidy/sets_with_plausible_values.rds")
dataComplete <- readRDS("data/tidy/dataComplete.rds")
```

<br>

# Quantile Regressions

## Functions

### write_formula()

These are the models ranging from least to most complex.

```{r}
write_formula <- function(domain) {
  formula_0 <<- paste0(domain, " ~ 1")
  formula_1 <<- paste0(domain, " ~ age")
  formula_2 <<- paste0(domain, " ~ age + sex")
  formula_3 <<- paste0(domain, " ~ age + country")
  formula_4 <<- paste0(domain, " ~ age + sex + country")
  formula_5 <<- paste0(domain, " ~ age + I(age_50^2) + country + sex -1")
  formula_6 <<- paste0(domain, " ~ age + sex + country + country:sex + country:age")
  formula_7 <<- paste0(domain, " ~ age * sex * country")
}
```

<br>

### fit_model()

Function to calculate all 25 models and save tau, parameter name, value
```{r}
fit_model <- function(data, formula) {
  fit <- rq(data = data, 
            formula, 
            tau = c(.01, .05, .1, .2, .3, .4, .5, .6, .7, .8, .9, .95, .99 ))
  
  ldply(summary(fit, se = "nid"), function(x) data.frame(tau = x$tau, 
                                                         par = rownames(x$coef),
                                                         est = x$coef[, 1],
                                                         se = x$coef[, 2]))
  
}
```

<br>

### get_pooled()
```{r}
get_pooled <- function(x) {
  x <- mi.meld(q = as.matrix(x$est), 
               se = as.matrix(x$se))
  
  return(data.frame(est = x[[1]], 
                    se = x[[2]]))
}
```

<br>

### get_model_fit()
```{r}
get_model_fit <- function(data, formula) {
  
  fit <- rq(data = data, 
            formula, 
            tau = c(.01, .05, .1, .2, .3, .4, .5, .6, .7, .8, .9, .95, .99 ))
  
  nobs <- nrow(residuals(fit))
  
  ldply(fit, function(x) data.frame(tau = c(.01, .05, .1, .2, .3, .4, .5, .6, .7, .8, .9, .95, .99), 
                                    AIC = AIC(fit)[1:13],
                                    BIC = AIC(fit, k = log(nobs))[1:13]))
  
}
```

<br>

# Create all models for all domains and save AIC/BIC 

We use `age_50` for all our analyses. This is standardized for age - 50, as we use this for the baseline.
```{r}
domains <- c("pf_pv", "ue_pv", "pi_pv")

formulas <- c(paste0("formula_", 0:7))

models_age_50 <- list()

for (k in domains) {
  
  formula_0 <<- paste0(k, " ~ 1")
  formula_1 <<- paste0(k, " ~ age_50")
  formula_2 <<- paste0(k, " ~ age_50 + sex")
  formula_3 <<- paste0(k, " ~ age_50 + country")
  formula_4 <<- paste0(k, " ~ age_50 + sex + country - 1")
  formula_5 <<- paste0(k, " ~ age_50 + I(age_50^2) + country + sex -1")
  formula_6 <<- paste0(k, " ~ age_50 + sex + country + country:sex + country:age_50")
  formula_7 <<- paste0(k, " ~ age_50 * sex * country")
  
  for (i in formulas) {
    
    # calculate 25 quantile regression
    model <- ldply(sets_with_plausible_values, 
                   function(dat) fit_model(data = dat,
                                           formula = eval(parse(text = i))))
    # save model in list object
    models_age_50[[k]]$model[[i]] <- model
    
    # save AIC and BIC
    models_age_50[[k]]$AIC[[i]] <- ldply(sets_with_plausible_values, 
                                  function(dat) get_model_fit(data = dat,
                                                              formula = eval(parse(text = i)))) %>% 
      filter(.id == "coefficients") %>% 
      mutate(id = rep(1:25, each = 13)) %>% 
      select(id, tau, AIC, BIC)
    
    # save pooled model
    models_age_50[[k]]$pooled[[i]] <- model %>% 
      group_by(tau, par) %>% 
      do((get_pooled(.)))
  }
}
```

<br>

# Save all models
```{r}
write_rds(models_age_50, "data/tidy/models_age_50.rds")
```

```{r reproducibility_stuff, include=FALSE}
devtools::session_info() %>%
    yaml::write_yaml("code reproducibility/sessioninfo_2.yaml")
```